Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-06 volunteer-clouds-ieee-ci-si.tex

\begin{figure}[!t]
\centering
\includegraphics[width=12cm]{img/baseline-times.png}
\caption{Comparison of time to solution for the baseline system, using a {\tt
    node.js} client, for different population sizes. They only compare on
runs in which solution has been found.}
\label{fig:baseline}
\end{figure}
First we establish the baseline performance by running the
evolutionary algorithm in a desktop client written using NodEO, 
%FERGU: es NodEO o NodIO? Quito el \sf, por cierto, que queda feo
%Por qué usamos NodEO aquí y no NodIO, vamos a compararlos? 
%Qué diferencias hay entre los dos? (ponerlo en el SOA)
the node.js evolutionary algorithm library. This experiment tries to 
%FERGU: quitar el "the node.js evolutionary algorithm library", si ya lo hemos dicho
%o explicarlo mejor: "the basic js library we have used as base to built NodIO", por ejemplo
find the solution to the 40-trap function with parameters $l=4, a=1,
b=2, z=3$, a population size equal 512, which was found in previous
experiments to be the correct one for finding the solution 95\% of the
%Fergu: cita a esos experimentos?
time. The algorithm was run until the solution (a string with all
ones) was found or five millions evaluations had been performed. It
took around a minute, on average, that is $68.9694$ seconds, to
perform the fifty runs. In this experiment only 33, that is, 66\% were
successful. The experiments were repeated for population $p=1024$,
with success rate upgraded to 100\% and average duration $3.46
seconds$. Results for these two experiments 
are shown in Figure \ref{fig:baseline}.

@@

Initial experiments were set up using the OpenShift
Platform-as-a-Service, which provides a free tier within which this
experiment could be performed. That way, and as required, the hardware
and cloud cost for this experiment were zero. Experiments were
announced through a post in Twitter and other social networks, and
results were published here \cite{DBLP:conf/gecco/GuervosG15}. For the
purpose of this paper, we repeated the announcement several times
through the months of April and then by the beginning of August.

>>>>

\begin{figure}[!t]
\centering
\includegraphics[width=12cm]{img/baseline-times.png}
\caption{Comparison of time to solution for the baseline system, using a {\tt
    node.js} client, for different population sizes. They only compare on
runs in which solution has been found.}
\label{fig:baseline}
\end{figure}
First we establish the baseline performance by running the
evolutionary algorithm in a desktop client written using NodEO, 
%FERGU: es NodEO o NodIO? Quito el \sf, por cierto, que queda feo
%Por qué usamos NodEO aquí y no NodIO, vamos a compararlos? 
%Qué diferencias hay entre los dos? (ponerlo en el SOA)
the node.js evolutionary algorithm library. This experiment tries to 
%FERGU: quitar el "the node.js evolutionary algorithm library", si ya lo hemos dicho
%o explicarlo mejor: "the basic js library we have used as base to built NodIO", por ejemplo
find the solution to the 40-trap function with parameters $l=4, a=1,
b=2, z=3$, a population size equal 512, which was found in previous
experiments to be the correct one for finding the solution 95\% of the
%Fergu: cita a esos experimentos?
time. The algorithm was run until the solution (a string with all
ones) was found or five millions evaluations had been performed. It
took around a minute, on average, that is $68.9694$ seconds, to
perform the fifty runs. In this experiment only 33, that is, 66\% were
successful. The experiments were repeated for population $p=1024$,
with success rate upgraded to 100\% and average duration $3.46$
seconds. Results for these two experiments 
are shown in Figure \ref{fig:baseline}.

@@

Initial experiments were set up using the OpenShift
Platform-as-a-Service, which provides a free tier within which this
experiment could be performed. That way, and as required, the hardware
and cloud cost for this experiment were zero. Experiments were
announced through a post in Twitter and other social networks, and
results were published here \cite{DBLP:conf/gecco/GuervosG15}. For the
purpose of this paper, we repeated the announcement several times
through the months of April and then by the beginning of August. All
in all, we have the set of runs with the characteristics shown in
Table \ref{tab:runs}.
%
\begin{table*}
\caption{Characteristics of the volunteer computing initial runs. \label{tab:runs}}
\begin{center}
\begin{tabular}{l|rr}
\hline
Date & \# experiments & Different IPs \\
\hline 
April 4th 4/4 & 57 & 191 \\
April 24th 4/24 &  231 & 559 \\
July 31th 7/31 & 97 & 179 \\
\hline 
\end{tabular}
\end{center}
\end{table*}
%
\begin{table*}
\caption{Summary of time per run, number of IPS and number of {\tt
    PUT}s per IP in the initial runs. \label{tab:summary}}
\begin{center}
\begin{tabular}{l|ccccc}
\hline
Date & Median \#IPs & Median time (s) & Median \#{\tt PUT}s & $<$ 69s & $<$ 3.46s \\
\hline 
4/4 & 5 & 2040 & 18 & 14.29\% & 5.36\% \\
4/24 &  5 & 732 & 11 & 47.39\% & 3.91\% \\
7/31 & 5 & 260 & 23 & 27.08\% & 1.04\%  \\
\hline 
\end{tabular}
\end{center}
\end{table*}
%
A summary of the characteristics of each run is also shown in Table
\ref{tab:summary}.
